The title

### 2018-04-08 writeup.Rmd
binary plot

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Second Author"
    affiliation   : "1"
  - name          : "Third Author"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Stanford University"

author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no

class             : "man"
output            : papaja::apa6_pdf
---

```{r load_packages, include = FALSE}
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(lme4)
library(ggthemes)
library(forcats)
library(brms)
```

@@

# changing trial type names to adhoc vs. scalar
implicature_rate$trial_type <-fct_recode(pragmatic_trials$trial_type, 
                                         adhoc = "XY_X", scalar = "XY_XorY")
```

* No data will be excluded.

@@

100 participants (20 per condition) were recruited using Amazon Mechanical Turk.

@@

* The study used five different types of measurements. 1. two-options (true vs. false) 2. two-options (wrong vs. right) 3. three-options (wrong, neither, right) 4. four-options (wrong, kinda wrong, kinda right, right) 5. five-options (wrong, kinda wrong, neither, kinda right, right).

@@

We are primarily concerned with the rate of implicatures in an experimental study. Two trial types are predicted to include pragmatic implicatures. First, trials where there are two animals on the card but the fictional character guesses using the connective *or*; for example "cat or dog" when the card has both a cat and a dog on it. We call such trials "scalar" trials. Second, trials where there are two animals on the card but the character guesses only one; for example "cat" when the card has a cat and a dog on it. We call such trials "exhaustive". In our assessment of implicature rate we focus on these two types of trials.

@@

Second, ...

@@

@@

```{r}
implicature_analysis_a <- glmer(implicature ~ definition * response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)

@@

implicature_analysis_b <- brm(implicature ~ definition * response_type * trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
```

>>>>

---
title             : "The title"
shorttitle        : "Title"
author:

  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Second Author"
    affiliation   : "1"
  - name          : "Third Author"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "Stanford University"
author_note: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  Enter abstract here. Each new line herein must be indented, like this line.

keywords          : "keywords"
wordcount         : "X"
bibliography      : ["r-references.bib"]
figsintext        : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
class             : "man"
output            : papaja::apa6_pdf
editor_options: 
  chunk_output_type: console
---

```{r load_packages, include = FALSE}
library(grid)
library(gtable)
library(papaja)
library(tidyverse)
library(magrittr)
library(readr)
library(png)
library(jpeg)
library(lme4)
library(ggthemes)
library(forcats)
library(brms)
```

@@

# changing trial type names to exhaustive vs. scalar
implicature_rate$trial_type <-fct_recode(pragmatic_trials$trial_type, 
                                         exhaustive = "XY_X", scalar = "XY_XorY")
```

@@

100 participants (20 per condition) were recruited using Amazon Mechanical Turk. No participant was excluded from the final analysis.

@@

The study used five different types of measurements. 1. two-options (true vs. false) 2. two-options (wrong vs. right) 3. three-options (wrong, neither, right) 4. four-options (wrong, kinda wrong, kinda right, right) 5. five-options (wrong, kinda wrong, neither, kinda right, right).

@@

We are primarily concerned with the "rate of implicatures" in an experimental study. Two trial types are predicted to include pragmatic implicatures. First, trials where there are two animals on the card but the fictional character guesses using the connective *or*; for example "cat or dog" when the card has both a cat and a dog on it. We call such trials "scalar" trials. Second, trials where there are two animals on the card but the character guesses only one; for example "cat" when the card has a cat and a dog on it. We call such trials "exhaustive". In our assessment of implicature rate we focus on these two types of trials.

@@

A second hypothesis was that the definition of what responses count as participants computing an implicature may affect the estimated rate of implicature in the experimental task.

@@

```{r binaryPlot, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=8, fig.height=4, set.cap.width=T, num.cols.cap=1, fig.cap = "Adults' two-alternative forced choice judgments in the connective guessing game."}

binary_summary<-
  data %>%
  filter(response_type=="binary") %>%
  group_by(card_type, guess_type, response) %>%
  summarize(count=n()) %>%
  group_by(card_type, guess_type) %>%
  mutate(total = sum(count), proportion=count/total)

binary_summary$response <- factor(binary_summary$response, levels = c("wrong","right"))
binary_summary$guess_type <- factor(binary_summary$guess_type, levels = c("Z","X","XandY","XorY"))
binary_summary$guess_type <- recode(binary_summary$guess_type, Z = "elephant", X = "cat", XandY = "cat and dog", XorY ="cat or dog")

binary_plot<-
  binary_summary %>%
  ggplot(aes(x=response, y=proportion, fill=response)) +
  geom_bar(stat = "identity", position="dodge", width = 0.6) +
#  geom_linerange(aes(ymax=cih, ymin=cil), position= position_dodge(width=0.9)) + 
  facet_grid(card_type~guess_type) +
  labs(x="", y="")+
  theme_few() +
  theme(text = element_text(size=17)) +
  scale_fill_manual(values = c("red4", "springgreen3"), guide=FALSE)

cat <- 
  readJPEG("experiments/figs/cat_card.jpg") %>%
  rasterGrob(width=0.9)

cat_dog <- 
  readJPEG("experiments/figs/catdog_card.jpg")%>%
  rasterGrob(width=0.9)

binary_plot_g <- ggplot_gtable(ggplot_build(binary_plot))

strips <- grep("strip-r", binary_plot_g$layout$name)

new_grobs <- list(cat, cat_dog)

binary_plot_g <- with(binary_plot_g$layout[strips,],
          gtable_add_grob(binary_plot_g, new_grobs,
                          t=t, l=l, b=b, r=r, name="cards"))        
binary_plot_g$widths[[11]] <- unit(2.5,"cm")

grid.draw(binary_plot_g)
```

@@

```{r}
implicature_rate$card <- implicature_rate$card %>% tolower()

implicature_analysis_a <- glmer(implicature ~ definition * response_type + trial_type + (1+response_type|card) + (1|participant), family="binomial", data=implicature_rate)

@@

implicature_analysis_b <- brm(implicature ~ definition * response_type + trial_type + (1+response_type|trial_type) + (1|participant), family="binomial", data=implicature_rate)
```
